Signal2Image Modules in Deep Neural Networks for EEG Classification

### 2023-11-13 latex/ms.tex
.

\title{Signal2Image Modules in Deep Neural Networks for EEG Classification}
\author{Paschalis Bizopoulos, George I. Lambrou and Dimitrios Koutsouris%
\thanks{The authors are with Biomedical Engineering Laboratory, School of Electrical and Computer Engineering, National Technical University of Athens, Athens 15780, Greece e-mail: {\tt\small pbizopoulos@protonmail.com}, {\tt\small glamprou@med.uoa.gr}, {\tt\small dkoutsou@biomed.ntua.gr.}}
}

>>>>

\title{Signal2Image Modules in Deep Neural Networks for EEG Classification}
\author{Paschalis Bizopoulos, George I. Lambrou and Dimitrios Koutsouris%
\thanks{The authors are with Biomedical Engineering Laboratory, School of Electrical and Computer Engineering, National Technical University of Athens, Athens 15780, Greece e-mail: {\tt\small pbizop@gmail.com}, {\tt\small glamprou@med.uoa.gr}, {\tt\small dkoutsou@biomed.ntua.gr.}}
}
